### 2021-02-16 paper.Rmd
assigning tasks

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    email: stuart.a.lee@monash.edu
  - name: Ursula Laa 
    affiliation: Monash University
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
title:
  formatted: "An Overview of Tours for Dynamic Visualisation of High-dimensional Data"
  type: "Advanced Review"
abstract: > 
  Abstract goes here.
keywords:
  formatted: ["tours", "data visualisation"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
    citation_package: natbib
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

@@

- Purpose/why and what is high-d data
- Original tours
- Dataviewer, XGobi, GGobi, cranvas (XLispStat, Orca, mmvz) (Di)
- Alternatives (Stuart)

@@

- Bases notation
- Display
- Choosing targets, inc pp indexes
- Geodesic interpolation
- Slices vs projections
- Transformations on projections

@@

- Stop/start/reverse
- Manual (Nick)
- Linked brushing (Earo)
- Spin-and-brush

@@

- tourr
- liminal
- python

@@

- Model vis (from Hadley, removing the blidnfold)
- Physics (Ursula)
- Bioinformatics (Stuart)
- High-d shapes/distributions

>>>>

---
author:
  - name: Stuart Lee
    affiliation: Monash University
    # use this syntax to add text on several lines
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    email: stuart.a.lee@monash.edu
  - name: Ursula Laa 
    affiliation: 
    address: |
      | Department of  ,
      |  University
  - name: Dianne Cook
    address: |
      | Department of Econometrics and Business Statistics,
      | Monash University
    affiliation: Monash University
    email: dicook@monash.edu
title:
  formatted: "An Overview of Tours for Dynamic Visualisation of High-dimensional Data"
  type: "Advanced Review"
abstract: > 
  Abstract goes here.
keywords:
  formatted: ["tours", "data visualisation"]
output: 
  bookdown::pdf_document2:
    template: template/wires_template_rmd.tex
    keep_tex: true
    toc: false
    citation_package: natbib
bibliography: references.bib
biblio-style: apalike
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.show = 'hold',
  dpi = 300 #,
  # out.width = "\\textwidth",
  # fig.path = here::here('img/')
)
```

<!--
Writing style: third person (it was done, ...)
-->

@@

- Purpose/why and what is high-d data (Di)
- Original tours (Di)
- Dataviewer, XGobi, GGobi, cranvas (XLispStat, Orca, mmvz) (Di)
- Alternatives (Stuart)

@@

- Bases notation (Sherry)
- Display (Sherry)
- Choosing targets, inc pp indexes (Sherry)
- Geodesic interpolation (Ursula)
- Slices vs projections (Ursula)
- Transformations on projections (Ursula)

@@

- Stop/start/reverse
- Manual (Nick)
- Linked brushing (Earo)
- Spin-and-brush  (Ursula)

@@

- tourr (Di) and spinifex (Nick)
- liminal (Stuart)
- python (Di to follow up with Csaba)

@@

- Model vis examples eg random forest (from Hadley, removing the blindfold) (Natalia)
- Physics (Ursula)
- Bioinformatics (Stuart)
- High-d shapes/distributions: normal, skewed, outliers, (Di from tutorial notes)
